\section{sketches}

Approximate programming-by-example combines reasoning-based program search with numerical search methods from machine learning.
The high-level idea is to get shrink the search space as much as possible with formal methods, then switch over to machine learning.


\subsection{preliminaries}
A \textit{Metric Space} is a pair $(M,d)$, where S is a set and $d:M \times M \to \reals$ is a distance metric between all points in the set. The metric $d$ must obey some properties that are listed on wikipedia...

\iffalse
I think I dont need this actually
A product metric $(X^{*},d_p)$ is a metric space over the Cartesian product of finitely many metric spaces $(X_0,d_0),...,(X_n,d_n)$,
  where $d_p:X^n \times X^n \to \reals$ also obey those properties.
If $d_p$ is a norm ``which is non-decreasing as the coordinates of a positive n-tuple increase``\footnote{took this from \url{https://en.wikipedia.org/wiki/Metric_space#Product_metric_spaces}, not sure how to formalize it yet}, then then topology of the X^* is equivelant
\fi

\subsection{new stuff}
\samepage{
Given:
\begin{itemize}
  \item A metric space $(M^{*},C)$ 
  \item A set of input,output examples $\{(i_0,o_0),...,(i_n,o_n)\}$ where $i_j,o_j \in M^{*}$
  \item A grammar $G$ where elements of the grammar are functions $M^{*} \to M^{*}$
\end{itemize}
Find $p \in G$ that minimizes $\sum_{j=0}^{n} \ C(o_j,p(i_j))$.
}

This is a problem well-suited for machine learning, unless $C$ is prohibitively expensive to repeatedly recompute.
Machine learning approaches (like gradient descent) require generating and testing many possible $p \in G$.
In this case, we want to use formal methods to shrink $G$ to a new, smaller grammar $G' \subset G$ \markk{how to I properly write down that the words generated by $G'$ are a subset of the words generated by $G$}.

To do this we also need a set of metric spaces $(M_0,d_0),...,(M_m,d_m)$, where the sets $M_0,..,M_m$ are built from the projections ($proj_i:M^{*} \to M_i$ into lower dimensional spaces (\markk{how to formalize this?})

The user then provides a selection of dimension $i,j$ \markk{these don't need to be contiguous} and a grammar transformation $t:G \to G$ where $0 \geq i \geq j \geq m$, $t(g) \subset g$, where $N$ is the Euclidean norm,

\begin{align*}
  N\big{(} d_i(proj_i(i),proj_i(o)) ,..., d_j(proj_j(i),proj_j(o)) \big{)} > 0 \\
\implies \\
\forall p \in G'.\ C(o,p(i)) > 0 \\
\end{align*}

This means, the user tells us if the input/output examples have some relation in the $[i,j]$ dimensions, then we can 'cut off' part of the search space.

\markk{The main problem I am stuck on right now is that I don't know how to formalize a transformation on grammars.}
\markk{also Im not so sure about the >0 part above - but its something like that}

